Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{float}
\usepackage[noadjust]{cite}

@@

\author{
\IEEEauthorblockN{Joel Pepper}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0002-1601-8729}
\and
\IEEEauthorblockN{Jane Greenberg}
\IEEEauthorblockA{\textit{Department of Information Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0001-7819-5360}
\and
\IEEEauthorblockN{Yasin Baki\c{s}}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0001-6144-9440}
\and
\IEEEauthorblockN{Xiaojun Wang}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0001-8639-6795}
\and
\IEEEauthorblockN{Henry Bart Jr.}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0002-5662-9444}
\and
\IEEEauthorblockN{David Breen}
\IEEEauthorblockA{\textit{Department of Information Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0002-1376-5008}
}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%}

@@

\section{Introduction}
\begin{figure}[H]
  \centering
  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
  \hspace{4mm}
  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
  \label{fig:teaser}
\end{figure}
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens. Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens. These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
%{jane} not sure this following mine: "As researchers seek to apply computational methods, and explore AI, significant challenges surface..)" 
%should we try to insert machine learning here?

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% REMOVE FOLLOWING LINE BEFORE SUBMITTING %%%%%%%%%
\setlength {\marginparwidth }{2cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{float}
\usepackage[noadjust]{cite}

@@

\author{
\IEEEauthorblockN{Joel Pepper}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0002-1601-8729}
\and
\IEEEauthorblockN{Jane Greenberg}
\IEEEauthorblockA{\textit{Department of Information Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0001-7819-5360}
\and
\IEEEauthorblockN{Yasin Baki\c{s}}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0001-6144-9440}
\and
\IEEEauthorblockN{Xiaojun Wang}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0001-8639-6795}
\and
\IEEEauthorblockN{Henry Bart Jr.}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0002-5662-9444}
\and
\IEEEauthorblockN{David Breen}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0002-1376-5008}
}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%}

@@

\section{Introduction}
\begin{figure}[H]
  \centering
  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
  \hspace{4mm}
  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
  \label{fig:teaser}
\end{figure}
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.\cite{page2015digitization,}. These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
%{jane}should we try to insert machine learning here, last sentence, or computation methods ok?
